---
title: "Section 7"
author: "Masaoud"
date: "4/5/2023"
output: pdf_document
---

## Info

- Thu: OH on Tuesday 9-10:30am in SC 316.06. Section on Thursday 1:30-2:30 PM SC 705.
- Masaoud: OH on Tuesday 9-10:30pm in Kirkland Dhall. Section on Friday 12-1pm in Sever 209.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\textbf{We will try to leave some time at the end to answer any questions about projects (for Thu's section only) and/or problem set 6.}

We will now include a very high-level overview of the material after functions but before R packages (the next section will go over R packages). Please let us know what questions you have!

- One way we can reduce duplication is through iteration. There are a few different types of iteration.
  - You can iterate in \texttt{dplyr}; some useful functions for this are \texttt{across()} (enumerating each column you want to work with), \texttt{everything()} (working with every column), and \texttt{where()} (specifying conditions of columns that you want to work with). An anonymous function is often used as an input to specify what you exactly want to do with a column, and we use ~ and .x when calling anonymous function (see lecture slides).
  - You can also iterate explicitly using loops. \texttt{for()} loops are for when we know the exact number of iterations we need, whereas \texttt{while()} will repeat until a certain condition is not met. 
  - Finally, you can improve functional programming (functions that allow us to pass other functions as arguments) with iteration using the \texttt{purrr} package.
  
- We also learned about refactoring code.




\newpage 

## Loops


```{r}
ggplot(mtcars, aes(x = mpg)) + geom_histogram()
ggplot(mtcars, aes(x = cyl)) + geom_histogram()
ggplot(mtcars, aes(x = disp)) + geom_histogram()
ggplot(mtcars, aes(x = hp)) + geom_histogram()
ggplot(mtcars, aes(x = drat)) + geom_histogram()
ggplot(mtcars, aes(x = wt)) + geom_histogram()
ggplot(mtcars, aes(x = qsec)) + geom_histogram()
ggplot(mtcars, aes(x = vs)) + geom_histogram()
ggplot(mtcars, aes(x = am)) + geom_histogram()
ggplot(mtcars, aes(x = gear)) + geom_histogram()
ggplot(mtcars, aes(x = carb)) + geom_histogram()
```


```{r}
ggplot(mtcars, aes(x = mpg)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = cyl)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = disp)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = hp)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = drat)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = wt)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = qsec)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = vs)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = am)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = gear)) + geom_histogram(fill = "blue")
ggplot(mtcars, aes(x = carb)) + geom_histogram(fill = "blue")
```

You can already see how every edit is exausting. Refactor the code to solve this problem. 

```{r}

```


\newpage

## Map

Figure our what this code is doing. Refactor it:
- Using mapping instead of a loop.
- Renaming variables
- Renaming rows and columns

```{r}
x = matrix(nrow = length(names(mtcars)), ncol = length(names(mtcars)))
for (i in 1:length(names(mtcars))){
  for (j in 1:length(names(mtcars))){
    x[i, j] = cov(mtcars[i], mtcars[j])
  }
}
x
```





