---
title: "section 2"
author: "Masaoud AND Thu"
date: "February 16 and 17, 2023"
output: pdf_document
---

## Info

- Thu: OH on Tuesday 9-10:30am in SC 316.06. Section on Thursday 1:30-2:30 PM SC 705.
- Masaoud: OH on Tuesday 9-10:30pm in Kirkland Dhall. Section on Friday 12-1pm in Sever 209.

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(ggplot2)
library(dplyr)
```

This section will primarily focus on helping you practice Data Joins and Reshaping, but we welcome any questions about git, vectors, and lists (including how to work with the nested structure).

## Vectors

Pick your favorite five classes at Harvard (Stat 108 has to be one of them). Create three vectors: one for the numbers of the classes (Stat108, Stat101, ...), one for the semester when you took it (fall/spring), and one for the year when you took it. 


```{r}
classes <- NA
semesters <- NA
years <- NA
```

## Dataframe

Create a data frame of the previous vectors

```{r}

```






