---
title: "section 4"
author: "Masaoud AND Thu"
date: "February 23 and 24, 2023"
output: pdf_document
---

## Info

- Thu: OH on Tuesday 9-10:30am in SC 316.06. Section on Thursday 1:30-2:30 PM SC 705.
- Masaoud: OH on Tuesday 9-10:30pm in Kirkland Dhall. Section on Friday 12-1pm in Sever 209.

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(ggplot2)
library(dplyr)
library(spData)
library(sf)
library(readr)
```

We are using a US States Shapefile that is built into R. We load it here. Play around with the data and plot a blank map below.

```{r}
# load in US States Data
data(us_states)
# TODO: generate blank map here.
ggplot(data = us_states, 
       mapping = 
         aes(geometry = geometry)) + 
  geom_sf() +
  coord_sf() +
  theme_void()
```

Now, we'll load in some data about the presidential elections from 1976-2020.

```{r}
presidents <- read_csv("https://raw.githubusercontent.com/mtpham17/108section2023/main/section%204/presidents.csv")
```

Find an election year you are interested in. Select it (and do appropriate data wrangling) so that you can merge the relevant presidents data with your shapefile of the United States Map.

```{r}
## Data Wrangling
presidents_2016 <- presidents %>%
  filter(year == 2016) %>%
  select(state, party_detailed, candidatevotes, totalvotes) %>%
  filter(party_detailed %in% c("REPUBLICAN", "DEMOCRAT")) %>%
  mutate(candidate_ratio = candidatevotes/totalvotes) %>%
  group_by(state, party_detailed) %>%
  summarize(total_party_ratio = sum(candidate_ratio)) %>%
  ungroup()

us_states_merge <- us_states %>%
  mutate(NAME = toupper(NAME)) 

us_states_votes <- right_join(us_states_merge, presidents_2016, by = c("NAME" = "state"))
us_states_democrats <- us_states_votes %>%
  filter(party_detailed == "DEMOCRAT")
```



Finally, make a plot of voting data with the US Map.

```{r}
## Plot of Election Data on Map
ggplot(data = us_states_democrats, 
       mapping = 
         aes(geometry = geometry,
             fill = total_party_ratio)) + 
  geom_sf() +
  coord_sf() +   
  theme_void()
```

