---
title: "section 5"
author: "Masaoud AND Thu"
date: "March 2 and 3, 2023"
output: pdf_document
---

## Info

- Thu: OH on Tuesday 9-10:30am in SC 316.06. Section on Thursday 1:30-2:30 PM SC 705.
- Masaoud: OH on Tuesday 9-10:30pm in Kirkland Dhall. Section on Friday 12-1pm in Sever 209.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\textbf{First: Any questions on projects? We can also answer any individual questions during the second half of our section!}

We will now include a very high-level overview of this week's material. Please let us know what questions you have!

\newpage

Now, we will practice with functions! This exercise was written by Prof. McConville. Solutions will be posted sometime before next week.

a.  Turn the following working code into an R function.  Make sure to give it a good name.


```{r, eval = TRUE}
library(pdxTrees)
pdxTrees <- get_pdxTrees_parks()
mean(is.na(pdxTrees$Tree_Height))
```




b. For the following function, `thing`, figure out what it is trying to do.  Then 

* Fix the function and argument names.
* Fix the order of the arguments.
* Fix defaults.
* Consider ways we could generalize the function.

```{r, eval = TRUE}
thing <- function(na.rm = FALSE, x = c(7, 1), y = c(3, 4)) {
  var1 <- mean(x, na.rm = TRUE)
  var2 <- mean(y, na.rm = TRUE)
  xx <- var(x, na.rm = TRUE)
  yy <- var(y, na.rm = TRUE)
  na <- length(x)
  nb <- length(y)
  df <- min(na, nb) - 1
  important_bit <- (var1 - var2 - 0)/sqrt(xx/na + yy/nb)
  pt(q = abs(important_bit), df = df, lower.tail = FALSE)*2
}
## Test it!
# Generate data for testing
x <- rnorm(n = 10)
y <- rnorm(n = 20, mean = 2)
# Test
thing(na.rm = TRUE, x = x, y = y)
thing(na.rm = FALSE)
```




