---
title: "section 5"
author: "Masaoud AND Thu"
date: "March 2 and 3, 2023"
output: pdf_document
---

## Info

- Thu: OH on Tuesday 9-10:30am in SC 316.06. Section on Thursday 1:30-2:30 PM SC 705.
- Masaoud: OH on Tuesday 9-10:30pm in Kirkland Dhall. Section on Friday 12-1pm in Sever 209.

\textbf{We will not have section not week (the week before spring break)! Good luck on your projects :)}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# load necessary packages here
library(stringr)
```


We will now include a very high-level overview of this week's material. Please let us know what questions you have!

- \textbf{Factors} are used to impose structure on categorical variables. The \textbf{levels} of a factor are the different values that a factor can take on. 
  - Some useful functions when working with factors are `fct_reorder()`, `fct_relevel()`, `fct_collapse()`, `fct_drop()`, and `fct_recode()`. There are others in lecture as well!
- We also learned how to manipulate strings with the package `stringr`. For example, you can make all letters in a string uppercase with `str_to_upper()`.
- On the topic of strings, sometimes we are interested in matching a particular pattern in a string. Kelly showed that it is not ideal to "hard code" the patterns we want to match (for example, if we want to match any numbers, we should not specify "0|1|2|...") because it's cumbersome and may fail to catch all the cases we want!
- This brings us to regular expressions, or regexes for short. Regexes are sequences of characters that specifies a pattern in a string, and they can be pretty general.
  - Feel free to use the physical "cheat sheet" from class. An online copy is also available here: https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_strings.pdf.

\newpage

Now, we will practice using Regular Expressions! Use `str_view_all()` to identify the pattern with a Regular Expression.


## Problem 1

For this problem we are going to use a subset of the character vector `fruit` that lives in `stringr`.

```{r}
set.seed(4433)
fruit_s <- sample(fruit, 20)
```


a. Highlight the pattern "berry".

```{r}

```

b. Now highlight all the fruits that contain the pattern "berry".  (Don't just highlight the word "berry").

```{r}

```

c. Highlight only fruits that contain "berry" and are one word.

```{r}

```

d. Highlight any repeated characters (e.g. "oo", "ll").

```{r}

```

e. Highlight fruits that start with a vowel.

```{r}

```

f. Highlight fruits that don't start with a vowel.

```{r}

```

g. Highlight the second to last character of fruits that end in a vowel.

```{r}

```


\newpage

## Problem 2

For this problem, let's continue to use these lyrics about numbers:

```{r}
lyrics <- c("But I would walk 500 miles",
            "2000 0 0 party over oops out of time!", 
            "1 is the loneliest number that you'll ever do",
            "When I'm 64",
            "Where 2 and 2 always makes a 5")
```



a. Locate all words that start with "w" or "W".


```{r}

```

b. Find all the non-numbers.

```{r}

```


c. Locate all the words that are at least five letters long.

```{r}

```

d. Locate all characters that appear after punctuation.

```{r}

```


e. Locate all the places where there are two vowels in a row.


```{r}

```

f. Find words that start with vowels.

Hint: Consider using `\\b` to find the start of the word.

```{r}

```




